OptiFit GLNE Exploratory

### 2021-04-03 exploratory/exploratory.Rmd

counts <- read_csv("./counts/all_counts.csv",col_names = c("sample","count"))

counts %>% 
  mutate(pct_mapped = count/10000) %>% 
  ggplot(aes(x=pct_mapped)) +
    geom_histogram(fill="grey",color="black") +
    theme_bw() + 
    scale_x_continuous(labels=scales::percent) +
    xlab("Percent of reads mapped")

# counts %>% 
#   mutate(pct_mapped = count/10000) %>% 
#   ggplot(aes(x="",y=pct_mapped)) +
#     geom_boxplot(fill="grey",color="black") +
#     theme_bw() +
#     xlab("")
```

@@

optifit_in_mcc <- read_tsv("./optifit_in_mcc.tsv")
optifit_out_mcc <- read_tsv("./optifit_out_mcc.tsv")
opticlust_mcc <- read_tsv("./opticlust_mcc.tsv")

mcc_data <- tibble(type=c(rep("OptiClust_489",nrow(optifit_out_mcc)),
                          rep("OptiFit_1",nrow(optifit_in_mcc)),
                          rep("OptiClust_all",nrow(opticlust_mcc))),
                   mcc=c(optifit_out_mcc$mcc,optifit_in_mcc$mcc,opticlust_mcc$mcc))

mcc_data$type <- factor(mcc_data$type,levels=c("OptiClust_all","OptiClust_489","OptiFit_1"))
mcc_data %>% 
  ggplot(aes(x=type,y=mcc,color=type)) + 
    geom_jitter(height=0) +
    xlab("") +
    theme_bw()

>>>>

fraction_mapped <- read_tsv("../results/tables/fraction_reads_mapped.tsv")

fraction_mapped %>% 
  ggplot(aes(x=fraction_mapped)) + 
    geom_histogram(fill="grey",color="black") +
  theme_bw() + 
  scale_x_continuous(labels=scales::percent) +
  xlab("Percent of reads mapped with cluster.fit") +
  ylab("number of samples")

@@

sensspec <- read_csv("../results/tables/merged_sensspec.csv")

mcc_data <- sensspec %>% 
  select(type,sample,mcc) %>% 
  mutate(type=factor(type,levels=c("opticlust","optifit_out","optifit_in"),labels=c("OptiClust_all","OptiClust_489","OptiFit_1")))

#mcc_data$type <- factor(mcc_data$type,levels=c("OptiClust_all","OptiClust_489","OptiFit_1"))
mcc_data %>% 
  ggplot(aes(x=type,y=mcc,color=type)) + 
    geom_jitter(height=0) +
    xlab("") +
    theme_bw()
